\begin{thebibliography}{9}

\bibitem{quique} Enric Herrera. \textit{Teor\'\i a Musical y Armon\'\i a Moderna, Vol 1 y 2}. Antoni Bosch, editor SA, 13 edition, 2004.

\bibitem{benson} Dave Benson. \textit{Mathematics and Music}. University of Georgia, \verb+http://www.math.uga.edu/~djb/html/math-music.html+, 2004.

\bibitem{hudak} Paul Hudak. \textit{Haskore Music Tutorial}. Yale University, Department of Computer Science, \verb+http://www.cs.lth.se/EDA120/assignment2/tutorial.pdf+, 2000.

\bibitem{bautista} Tomas Bautista, Tobias Oetiker, Huber Partl, Irene Hyna y Elisabeth Schlegl. \textit{Una Descripci\'on de \LaTeX 2$\varepsilon$}, Centro de Microelectr\'onica Aplicada de la Universidad de Las Palmas de Gran Canaria, 1996.

\bibitem{fokker} Jeroen Fokker. \textit{Functional Parsers}. Berlin, \verb+http://www.cs.uu.nl/people/jeroen/article/parsers/index.html+, 1995

\bibitem{lily} Han-Wen Nienhuys, Jan Nieuwenhuizen, Jurgen Reuter y Rune Zedeler. \textit{GNU LilyPond}. \verb+http://www.lilypond.org/doc/v2.0/+ \verb+Documentation/user/out-www/lilypond.pdf+, 2003.

\bibitem{teresita} Teresa Hortal\'a Gonz\'alez y Javier Leach Albert. \textit{Programaci\'on L\'ogica}. Universidad Complutense de Madrid, \verb+http://www.fdi.ucm.es/profesor/leach/PL/proglog.pdf+, 2004.

\bibitem{mario} Mario Rodr\'\i guez Artalejo. \textit{Programaci\'on Funcional}. Universidad Complutense de Madrid, \verb+http://www.fdi.ucm.es/profesor/mario/PF/cursoPF.pdf+, 2004

\bibitem{zvon} Miloslav Nic. \textit{Haskell reference}. \verb+http://zvon.org/other/haskell/+ \verb+Outputglobal/index.html+

\end{thebibliography}

